Eye in a Disk: eyeIntegration human eye and body transcriptome database version 1.00

### 2019-01-21 manuscript.Rmd
improve tsne zoom handling

tsne_zoom <- tsne_50_prep  %>% mutate(Group = case_when(study_accession == 'SRP012682' ~ 'GTEx',
                                                        TRUE ~ Tissue),
                                      Label = case_when(grepl('^0', Label) ~ '', TRUE ~ Label),
                                      Group = factor(Group, levels = c('GTEx', 'Cornea', 'ESC', 'Lens', 'Retina', 'RPE'))) %>% 
  filter(Group == 'Retina') %>%
  mutate( zoom = TRUE )

tsne_50_prep %>% mutate(Group = case_when(study_accession == 'SRP012682' ~ 'GTEx',
                                          TRUE ~ Tissue),
                        Label = case_when(grepl('^0', Label) ~ '', TRUE ~ Label),
                        Group = factor(Group, levels = c('GTEx', 'Cornea', 'ESC', 'Lens', 'Retina', 'RPE'))) %>% 
  ggplot(aes(x=X1,y=X2)) +
  scale_shape_manual(values=c(0:20,35:50)) +
  geom_point(size=6, alpha=0.1, aes(colour=Group)) +
  geom_point(size=1, alpha=0.6, position='jitter', aes(shape=Origin)) +
  xlab('t-SNE 1') + ylab('t-SNE 2') +
  facet_zoom(xy = Group == 'Retina', zoom.size = 1, zoom.data=zoom) +
  geom_label_repel(data=tsne_zoom,size = 7, aes(label=Label), alpha=0.7, box.padding = unit(0.3, "lines")) + 
  scale_color_discrete_sequential(palette = 'viridis') + 
  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  scale_fill_continuous(guide = guide_legend()) +
  theme(legend.position="bottom")
```

>>>>

retina_plus_group <- tsne_50 %>% filter(X1 > 34, X1 < 51, X2 > -25, X2 < 21)
dbscan_cluster <- dbscan(retina_plus_group %>%  select(X1, X2) ,  minPts = 3, eps = 2.0)

retina_plus_group$Cluster <- dbscan_cluster$cluster
col1 = 'X1'
col2 = 'X2'
# create label points for each cluster
cluster_centers <- retina_plus_group %>%
  left_join(.,core_tight_2019) %>% group_by(Cluster) %>%
  summarise(C1=mean(!!sym(col1)),C2=mean(!!sym(col2)),Tissue=paste(unique(Tissue),collapse=','))

# samples closest to center in each cluster
center_samples <- retina_plus_group %>% left_join(.,core_tight_2019)  %>%
  left_join(.,cluster_centers, by=c('Cluster')) %>%
  mutate(Distance = (!!sym(col1)-C1)+(!!sym(col2)-C2)) %>%
  group_by(Cluster) %>%
  dplyr::slice(which.min(Distance)) %>%
  dplyr::slice(1) %>% 
  .[['sample_accession']]

# cluster stats
cluster_stats <- retina_plus_group %>% left_join(.,core_tight_2019)  %>%
  mutate(Origin=factor(Origin, levels=c('Adult Tissue', 'Fetal Tissue', 'Stem Cell Line', 'Cell Line', 'Organoid'))) %>%
  mutate(Cluster = as.factor(Cluster)) %>%
  group_by(Cluster) %>%
  summarise(Cluster_Tissues = paste(unique(Tissue), collapse=',\n'), Cluster_Counts = paste(n(), ' samples', sep=''))

# set up for ggplot
retina_plus_group_prep <- retina_plus_group %>% 
  mutate(Origin=factor(Origin, levels=c('Adult Tissue', 'Fetal Tissue', 'Stem Cell Line', 'Cell Line', 'Organoid'))) %>%
  mutate(Cluster = as.factor(Cluster)) %>%
  select(-Cluster_Tissues) %>% 
  left_join(., cluster_stats, by=c('Cluster')) %>%
  mutate(Label = paste(Cluster, Cluster_Tissues,sep=': ')) %>%
  mutate(Label = ifelse(sample_accession %in% center_samples, Label, ""))

tsne_zoom <- retina_plus_group_prep  %>% 
  mutate(Group = case_when(study_accession == 'SRP012682' ~ 'GTEx',
                           TRUE ~ Tissue),
         Label = case_when(grepl('^0', Label) ~ '', TRUE ~ Label),
         Group = factor(Group, levels = c('GTEx', 'Cornea', 'ESC', 'Lens', 'Retina', 'RPE'))) %>% 
  mutate( zoom = TRUE )

tsne_50_prep %>% mutate(Group = case_when(study_accession == 'SRP012682' ~ 'GTEx',
                                          TRUE ~ Tissue),
                        Label = case_when(grepl('^0', Label) ~ '', TRUE ~ Label),
                        Group = factor(Group, levels = c('GTEx', 'Cornea', 'ESC', 'Lens', 'Retina', 'RPE'))) %>% 
  rowwise() %>% 
  mutate(Age = str_split(sample_attribute, '_')[[1]][2]) %>% 
  ggplot(aes(x=X1,y=X2)) +
  scale_shape_manual(values=c(0:20,35:50)) +
  geom_point(size=9, alpha=0.1, aes(colour=Group)) +
  geom_point(size=1, alpha=0.4, position='jitter', aes(shape=Origin)) +
  xlab('t-SNE 1') + ylab('t-SNE 2') +
  facet_zoom(xy = Group == 'Retina', zoom.size = 1, zoom.data=zoom, horizontal = F) +
  geom_label_repel(data=tsne_zoom,size = 2, aes(label=Label), alpha=0.7, box.padding = unit(0.3, "lines")) + 
  scale_color_discrete_sequential(palette = 'viridis') + 
  guides(colour = guide_legend(override.aes = list(alpha = 1))) 
```
